# echarts4r

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
library(htmltools)
library(echarts4r)

e_common(
    font_family = "Raleway"
)
```

[![Travis-CI Build Status](https://travis-ci.org/JohnCoene/echarts4r.svg?branch=master)](https://travis-ci.org/JohnCoene/echarts4r) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/JohnCoene/echarts4r?branch=master&svg=true)](https://ci.appveyor.com/project/JohnCoene/echarts4r) [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing) [![GitHub closed issues](https://img.shields.io/github/issues-closed/JohnCoene/echarts4r.svg)](https://github.com/JohnCoene/echarts4r/issues) [![code-size](https://img.shields.io/github/languages/code-size/JohnCoene/echarts4r.svg)](https://github.com/JohnCoene/echarts4r) [![activity](https://img.shields.io/github/last-commit/JohnCoene/echarts4r.svg)](https://github.com/JohnCoene/echarts4r) 

```{r, echo = FALSE}
div(
  class = "row",
  div(
    class = "col-md-4",
    img(
      src = "reference/figures/logo.png",
      class = "img-responsive responsive-img"
    )
  ),
  div(
    class = "col-md-8",
    p(
      "Powerful interactive visualisations in R."
    ),
    p(
      tags$a(
        tags$i(class = "fa fa-rocket"),
        class = "btn btn-success",
        href = "articles/get_started.html",
        style = "margin-bottom: 5px;",
        "Get Started"
      ),
      tags$a(
        tags$i(class = "fa fa-paint-brush"),
        class = "btn btn-primary",
        href = "articles/themes.html",
        style = "margin-bottom: 5px;",
        "Themes"
      ),
      tags$a(
        tags$i(class = "fa fa-play"),
        class = "btn btn-info",
        href = "articles/timeline",
        style = "margin-bottom: 5px;",
        "Timeline"
      ),
      tags$a(
        tags$i(class = "fa fa-desktop"),
        target = "_blank",
        class = "btn btn-default",
        href = "http://shiny.john-coene.com/echarts4rShiny",
        style = "margin-bottom: 5px;",
        "Shiny Demo"
      )
    )
  )
)
```

## Installation

The package is available on [CRAN](https://CRAN.R-project.org/package=echarts4r). The full installation can be obtained with:

```{r, eval=FALSE}
install.packages("echarts4r")
```

However, if you only want a _lite_ version you can simply do, this is useful for a lighter version that installs faster if you do not want to use any of the geospatial features of the package:

```{r, eval=FALSE}
install.packages("echarts4r", dependencies = c("Depends", "Imports"))
```

You can also install the _unstable_ development version of echarts4r with `remotes` from Github, see [changes](news/index.html).

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("JohnCoene/echarts4r") # github
```

## Companions

Companion packages to make `echarts4r` even better. You can install and load the whole suite with:

```{r, eval = FALSE}
remotes::install_github("JohnCoene/echarts4r.suite")
```

```{r, echo=FALSE}
div(
  class = "row",
  div(
    class = "col-md-6",
    div(
      class = "thumbnail",
      style = "text-align:center;",
      div(
        tags$i(class = "fa fa-globe fa-5x", style = "color:#293c55;"),
        class = "caption",
        h4(code("echarts4r.assets")),
        p("Icons, and assets for globes, add visually interesting globe overlays and background."),
        pre(class = "sourceCode r", code(class = "sourceCode r", "remotes::install_github('JohnCoene/echarts4r.assets')")),
        br(),
        p(
          htmltools::tags$a(
            href = "https://echarts4r-assets.john-coene.com/",
            target = "_blank",
            class = "btn btn-default",
            "Website"
          ),
          htmltools::tags$a(
            href = "https://github.com/JohnCoene/echarts4r.assets",
            target = "_blank",
            class = "btn btn-default",
            "Github"
          )
        )
      )
    )
  ),
  div(
    class = "col-md-6",
    div(
      class = "thumbnail",
      style = "text-align:center;",
      div(
        tags$i(class = "fa fa-map-o fa-5x", style = "color:#293c55;"),
        class = "caption",
        h4(code("echarts4r.maps")),
        p("A collection of 215 country maps to use with geo-spatial visualisations."),
        pre(class = "sourceCode r", code(class = "sourceCode r", "remotes::install_github('JohnCoene/echarts4r.maps')")),
        br(),
        p(
          htmltools::tags$a(
            href = "https://echarts4r-maps.john-coene.com/",
            target = "_blank",
            class = "btn btn-default",
            "Website"
          ),
          htmltools::tags$a(
            href = "https://github.com/JohnCoene/echarts4r.maps",
            target = "_blank",
            class = "btn btn-default",
            "Github"
          )
        )
      )
    )
  )
)
```

## Example

Create multiple charts, arrange them in a grid and connect their interactions; _this is nonsensical chart for demonstration purposes_.

```{r}
library(dplyr)
library(echarts4r)
library(echarts4r.assets)

e1 <- iris %>% 
  group_by(Species) %>% 
  e_charts(
    Sepal.Length,
    elementId = "chart"
  ) %>% 
  e_scatter(Petal.Length, Sepal.Width) %>% 
  e_datazoom(show = FALSE, y_index = 0) %>% 
  e_x_axis(min = 4) %>%  
  e_highlight(
    series_name = list("setosa", "versicolor", "virginica"), 
    btn = "high"
  ) %>% 
  e_downplay(
    series_name = list("setosa", "versicolor", "virginica"), 
    btn = "down"
  ) %>% 
  e_button(
    "high", "Highlight", 
    class = "btn btn-primary", 
    position = "bottom"
  ) %>% 
  e_button(
    "down", "Downplay", 
    class = "btn btn-default", 
    position = "bottom"
  ) %>% 
  e_legend(FALSE) %>% 
  e_title("Connect charts") %>% 
  e_tooltip(
    trigger = "item",
    axisPointer = list(
      type = "cross"
    )
  ) %>% 
  e_image_g(
    left = 50,
    top = 30,
    z = 999,
    style = list(
      image = "reference/figures/logo.png",
      width = 70,
      height = 75,
      opacity = .95
    )
  ) %>% 
  e_text_style(fontFamily = "Raleway")

e2 <- iris %>% 
  group_by(Species) %>%
  e_charts(Petal.Length) %>% 
  e_line(Sepal.Length) %>% 
  e_connect("chart") %>% 
  e_datazoom(y_index = 0) %>% 
  e_x_axis(min = 0) %>% 
  e_legend(
    bottom = 5,
    icons = ea_icons(
      c("warning", "signal", "photo")
    )
  ) %>% 
  e_tooltip(
    trigger = "item",
    axisPointer = list(
      type = "cross"
    )
  ) %>% 
  e_text_style(fontFamily = "Raleway")

e_arrange(e1, e2, rows = 1, cols = 2)
```
