# echarts4r

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)
library(htmltools)
library(echarts4r)
```

[![Travis-CI Build Status](https://travis-ci.org/JohnCoene/echarts4r.svg?branch=master)](https://travis-ci.org/JohnCoene/echarts4r) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/JohnCoene/echarts4r?branch=master&svg=true)](https://ci.appveyor.com/project/JohnCoene/echarts4r) [![Bitbucket Build Status](https://img.shields.io/bitbucket/pipelines/JohnCoene/echarts4r.svg)](https://bitbucket.org/JohnCoene/echarts4r) [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing) [![GitHub closed issues](https://img.shields.io/github/issues-closed/JohnCoene/echarts4r.svg)](https://github.com/JohnCoene/echarts4r/issues) [![echarts4r](https://cranlogs.r-pkg.org/badges/echarts4r)](https://CRAN.R-project.org/package=echarts4r)

```{r, echo = FALSE}
div(
  class = "row",
  div(
    class = "col-md-4",
    img(
      src = "reference/figures/logo.png",
      class = "img-responsive responsive-img"
    )
  ),
  div(
    class = "col-md-8",
    p(
      "Powerful interactive visualisations in R."
    ),
    p(
      tags$a(
        tags$i(class = "fa fa-rocket"),
        class = "btn btn-success",
        href = "articles/get_started.html",
        style = "margin-bottom: 5px;",
        "Get Started"
      ),
      tags$a(
        tags$i(class = "fa fa-paint-brush"),
        class = "btn btn-primary",
        href = "articles/themes.html",
        style = "margin-bottom: 5px;",
        "Themes"
      ),
      tags$a(
        tags$i(class = "fa fa-play"),
        class = "btn btn-info",
        href = "articles/actions-buttons",
        style = "margin-bottom: 5px;",
        "Buttons"
      ),
      tags$a(
        tags$i(class = "fa fa-desktop"),
        target = "_blank",
        class = "btn btn-default",
        href = "http://shiny.john-coene.com/echarts4rShiny",
        style = "margin-bottom: 5px;",
        "Shiny Demo"
      )
    )
  )
)
```

## Installation

The package is available on [CRAN](https://CRAN.R-project.org/package=echarts4r):

```{r, eval=FALSE}
install.packages("echarts4r")
```

You can also install the _unstable_ development version of echarts4r with `remotes` from Github, see [changes](news/index.html).

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("JohnCoene/echarts4r") # github
```

## Companions

Companion packages to make `echarts4r` even better.

```{r, echo=FALSE}
div(
  class = "row",
  div(
    class = "col-md-6",
    div(
      class = "thumbnail",
      style = "text-align:center;",
      div(
        tags$i(class = "fa fa-globe fa-5x", style = "color:#293c55;"),
        class = "caption",
        h4(code("echarts4r.assets")),
        p("Assets for globes, add visually interesting globe overlays and background."),
        pre(class = "sourceCode r", code(class = "sourceCode r", "remotes::install_github('JohnCoene/echarts4r.assets')")),
        br(),
        p(
          htmltools::tags$a(
            href = "https://echarts4r-assets.john-coene.com/",
            target = "_blank",
            class = "btn btn-default",
            "Website"
          ),
          htmltools::tags$a(
            href = "https://github.com/JohnCoene/echarts4r.assets",
            target = "_blank",
            class = "btn btn-default",
            "Github"
          )
        )
      )
    )
  ),
  div(
    class = "col-md-6",
    div(
      class = "thumbnail",
      style = "text-align:center;",
      div(
        tags$i(class = "fa fa-map-o fa-5x", style = "color:#293c55;"),
        class = "caption",
        h4(code("echarts4r.maps")),
        p("A collection of 215 country maps to use with geo-spatial visualisations."),
        pre(class = "sourceCode r", code(class = "sourceCode r", "remotes::install_github('JohnCoene/echarts4r.maps')")),
        br(),
        p(
          htmltools::tags$a(
            href = "https://echarts4r-maps.john-coene.com/",
            target = "_blank",
            class = "btn btn-default",
            "Website"
          ),
          htmltools::tags$a(
            href = "https://github.com/JohnCoene/echarts4r.maps",
            target = "_blank",
            class = "btn btn-default",
            "Github"
          )
        )
      )
    )
  )
)
```

## Example

Create multiple charts, arrange them in a grid and connect their interactions.

```{r}
library(echarts4r)

e1 <- iris %>% 
  group_by(Species) %>% 
  e_charts(
    Sepal.Length,
    elementId = "chart"
  ) %>% 
  e_scatter(Petal.Length, Sepal.Width) %>% 
  e_datazoom(show = FALSE, y_index = 0) %>% 
  e_x_axis(min = 4) %>% 
  e_highlight(series_name = list("setosa", "versicolor", "virginica"), btn = "high") %>% 
  e_downplay(series_name = list("setosa", "versicolor", "virginica"), btn = "down") %>% 
  e_button("high", "Highlight", class = "btn btn-primary", position = "bottom") %>% 
  e_button("down", "Downplay", class = "btn btn-default", position = "bottom") %>% 
  e_legend(FALSE) %>% 
  e_title("Connect charts")

e2 <- iris %>% 
  group_by(Species) %>% 
  e_charts(Sepal.Length) %>% 
  e_line(Petal.Length) %>% 
  e_connect("chart") %>% 
  e_datazoom(y_index = 0) %>% 
  e_x_axis(min = 4) %>% 
  e_legend(bottom = 5) 

e_arrange(e1, e2, rows = 1, cols = 2)
```
