---
title: "Actions & Buttons"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Actions & Buttons}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(echarts4r)
e_common(
    font_family = "Raleway"
)
```

Since version `1.2.0` one can add actions and optionally tie them to buttons.

## Actions

For instance once can use the `e_zoom` action to zoom on the graph (requires `e_datazoom` initialised).

```{r}
cars |> 
  e_charts(dist) |> 
  e_scatter(speed) |> 
  e_datazoom() |> 
  e_zoom(
    dataZoomIndex = 0,
    start = 20,
    end = 40
  ) 
```

## Buttons

Add a button to let the user trigger that action. We add a button with `e_button` and specify the id of our button in the action (`e_zoom`) so that the button knows which action to trigger.

```{r}
cars |> 
  e_charts(dist) |> 
  e_scatter(speed) |> 
  e_datazoom() |> 
  e_zoom(
    dataZoomIndex = 0,
    start = 20,
    end = 40,
    btn = "BUTTON"
  ) |> 
  e_button(
    id = "BUTTON", 
    htmltools::tags$i(class = "fa fa-search"), # passed to the button
    class = "btn btn-default",
    "Zoom in"
  )
```

You can also create the button elsewhere on the document, as long as the `id` matches the `btn`.

```{r}
value <- rnorm(10, 10, 2)

nodes <- data.frame(
  name = sample(LETTERS, 10),
  value = value,
  size = value,
  grp = rep(c("grp1", "grp2"), 5),
  stringsAsFactors = FALSE
)

edges <- data.frame(
  source = sample(nodes$name, 20, replace = TRUE),
  target = sample(nodes$name, 20, replace = TRUE),
  stringsAsFactors = FALSE
)

e_charts() |> 
  e_graph() |> 
  e_graph_nodes(nodes, name, value, size, grp) |> 
  e_graph_edges(edges, source, target) |> 
  e_focus_adjacency(
    seriesIndex = 0,
    dataIndex = 4,
    btn = "graphButton"
  ) 
```

Then create the button with id matching our event (`graphButton`).

```{r}
# create the button
htmltools::tags$a(
  id = "graphButton",
  class = "btn btn-primary",
  "Highlight node #4"
)
```

<span class="label label-warning"><i class="fa fa-warning"></i></span> Note that this means that each button in the document must bear a *unique* id.

You can also pass multiple buttons and change their positions.

```{r}
iris |> 
  group_by(Species) |> 
  e_charts(Sepal.Length) |> 
  e_line(Petal.Length) |> 
  e_datazoom() |> 
  e_highlight(series_name = "setosa", btn = "highlightButton") |> # highlight action
  e_zoom( # zoom action
    dataZoomIndex = 0,
    startValue = 4,
    endValue = 6,
    btn = "zoomBtn"
  ) |> 
  e_button(
    id = "zoomBtn",
    position = "bottom",
    class = "btn btn-primary",
    "Zoom"
  ) |> 
  e_button(
    "highlightButton",
    position = "bottom",
    class = "btn btn-default",
    "highlight"
  )
```

## All

Actions (all can be tied to buttons):

- `e_highlight` & `e_downplay` to highlight or downplay a serie.
- `e_showtip` & `e_hidetip` to show or hide the tooltip.
- `e_zoom` to zoom on a part of the graph.
- `e_visual_map_range` to select part of `e_visual_map`.
- `e_pie_select` & `e_pie_unselect` to select or unselect pie slices.
- `e_focus_adjacency` & `e_unfocus_adjacency` to focus or unfocus nodes on a graph.
- `e_legend_scroll`, `e_legend_toggle_select`, `e_legend_unselect` & `e_legend_select` to interact with the legend.
- `e_restore` to restore the chart.
- `e_map_select`, `e_map_unselect` & `e_map_toggle_select` to change maps.
