---
title: "Advanced"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(echarts4r)
```

This document details more advanced usage of the `echarts4r` package.

### coord.system

Chart types are not only applicable to the standard 2D cartesian coordinate system, though most charts will default to the `cartesian2d` coordinate system they may be applied to others.

Let's look at the heatmap. First a regular heatmap.

```{r}
v <- LETTERS[1:10]
matrix <- data.frame(
  x = sample(v, 300, replace = TRUE), 
  y = sample(v, 300, replace = TRUE), 
  z = rnorm(300, 10, 1),
  stringsAsFactors = FALSE
) %>% 
  dplyr::group_by(x, y) %>% 
  dplyr::summarise(z = sum(z)) %>% 
  dplyr::ungroup()

matrix %>% 
  e_charts(x) %>% 
  e_heatmap(y, z) %>% 
  e_visual_map(z)
```

One could also plot the heatmap on different coordinates, such as a calendar by first adding a calendar with `e_calendar` then specifying `coord.system = "calendar"`.

```{r}
dates <- seq.Date(as.Date("2018-01-01"), as.Date("2018-12-31"), by = "day")
values <- rnorm(length(dates), 20, 6)

year <- data.frame(date = dates, values = values)

year %>% 
  e_charts(date) %>% 
  e_calendar(range = "2018") %>% 
  e_heatmap(values, coord.system = "calendar") %>% 
  e_visual_map(max = 30)
```

Another example, using polar coordinates, plot a line on 2D cartesian coordinates, then change to polar.

```{r}
df <- data.frame(x = 1:10, y = seq(1, 20, by = 2))

df %>% 
  e_charts(x) %>% 
  e_line(y) 
```

```{r}
df %>% 
  e_charts(x) %>% 
  e_polar() %>% 
  e_angle_axis() %>% 
  e_radius_axis() %>% 
  e_line(y, coord.system = "polar", smooth = TRUE) 
```

There are numerous coordinate system available in `echarts4r`; `globe`, `cartesian3d` and `polar` **to name a few.**

### Customise the Axis

Use multiple axis.

```{r}
USArrests %>% 
  e_charts(Assault) %>% 
  e_line(Murder, smooth = TRUE) %>% 
  e_line(Rape, y.index = 1) %>%  # add secondary axis
  e_y_axis(spliLine = list(show = FALSE)) # hide split lines on first Y axis
```

### Flip coordinates

```{r}
data.frame(
  x = LETTERS[1:5],
  y = runif(5, 1, 15)
) %>% 
  e_charts(x) %>% 
  e_bar(y, name = "flipped") %>% 
  e_flip_coords() # flip axis
```

### Mark Points and Lines

Highlight points and lines on your plot.

```{r}
USArrests %>% 
  dplyr::mutate(
    State = row.names(.),
    Rape = -Rape
  ) %>% 
  e_charts(State) %>% 
  e_area(Murder) %>%
  e_bar(Rape, name = "Sick basterd", x.index = 1) %>% # second y axis 
  e_mark_line("Sick basterd", data = list(type = "average")) %>% 
  e_mark_point("Murder", data = list(type = "min"))
```

### Look for arguments

Look for more arguments, with `echarts4r` are often only one argument away from from what you want.

```{r}
df <- data.frame(
  parent = c("earth","earth","forest","forest","ocean","ocean","ocean","ocean"), 
  child = c("ocean","forest","tree","sasquatch","fish","seaweed","mantis shrimp","sea monster")
)

df %>% 
  e_charts() %>% 
  e_tree(
    parent, 
    child
  )
```

to radial:

```{r}
df %>% 
  e_charts() %>% 
  e_tree(
    parent, 
    child,
    layout = "radial" # radial
  )
```
