---
title: "Annotations"
author: "Jacci Ziebert"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Annotations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(echarts4r)
```

Annotations can be added to a variety of charts and with many styles. While Apache ECharts does not include a native annotation system, this is a custom function that creates annotations using SVG.

## Styling Annotation Elements

Here's an example of the style options. These take SVG attributes. Annotations can be removed by clicking the legend when `legend = TRUE`.

```{r}
iris |>
  e_charts(Sepal.Length) |>
  e_line(Sepal.Width) |>
  e_annotations(
    legend_color = "red",
    annotations = list(
      list(
        id = 0,
        x = 5,
        y = 3,
        text = '<b>HTML</b> <i>is supported!</i><br><span style="color:red">Red text</span>',
        offsetX = -40,
        offsetY = 40,
        # Using the styles
        group = list(draggable = TRUE, color = "red"),
        
        textStyle = list(
          "text-anchor" = "middle",
          "font-size" = 14,
          color = "green",
          dy = -5
        ),
        rectStyle = list(
          `stroke-dasharray` = c(35, 10),
          `stroke-width` = 2,
          # Shadow can be added!
          shadow = list(
            dx= 0,
            dy= 2,
            blur= 4,
            color= '#000',
            opacity= 0.3
          ),
          shape = list(width = 140, height = 50, r = 10)
        ),
        lineStyle = list(`stroke-width` = 6),
        arrowStyle = list(size = 18)
      )))
```

## Timeline

```{r}

iris |>
  group_by(Species) |>
  e_charts(Sepal.Length, timeline = TRUE) |>
  e_line(Sepal.Width) |>
  e_tooltip(trigger = "axis") |> 
  e_legend(orient = "vertical", top = "left") |> 
  e_annotations(
    annotations = list(
      list(
        id = 0,
        x = 1,
        y = 1,
        offsetY = -50,
        text = 'Same point!<br>Drag me!')))
```

## Facets
```{r}
group_size <- 20
n_groups <- 13
df <- data.frame("day" = rep(1:group_size, times=n_groups),
                 "temperature" = runif(group_size * n_groups, 10, 40),
                 "location" = rep(LETTERS[1:n_groups], each=group_size))

shape <- list(width = 50, height = 20)

df |>
  group_by(location) |>
  e_charts(day) |>
  e_line(temperature) |>
  e_facet(rows = 4, cols=4, legend_pos = "top", legend_space = 12) |>
  e_annotations(
    name = "Grid 12",
    grid = 12,
    annotations = list(
    list(
      x = 10,
      y = 30,
      text = 'Grid 12',
      textStyle = list("text-anchor" = "middle", "dominant-baseline" = "middle"),
      rectStyle = list(shape = shape)
      ))
    ) |> 
  e_annotations(
        name = "Grid 1",
        grid = 1,
        annotations = list(
          list(
            x = 10,
            y = 30,
            text = 'Grid 1',
            rectStyle = list(shape = shape)
            )))
```
## Shiny
Dragging the annotation can be captured.

```{r, eval=FALSE}
library(shiny)

ui <- fluidPage(
    echarts4rOutput("chart"),
      verbatimTextOutput("positions")
    )

server <- function(input, output, session) {
  output$chart <- renderEcharts4r({
    mtcars |>
      e_charts(mpg) |>
      e_scatter(wt) |>
      e_annotations(
            annotations = list(
              list(
                id = 1,
                x = 15,
                y = 3,
                text = 'An annotation'
              ),
              list(
                id = 999,
                x = 1,
                y = 1,
                text = 'Another'
              )
      ))
  })

  # Display positions when they drag
  output$positions <- renderPrint({
    input$chart_dragged_annotation
  })
}

shinyApp(ui = ui, server = server)
```


