---
title: "Connect"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Connect}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(htmltools)
library(echarts4r)
```

Since version `0.1.2` you can connect multiple two charts together which might make it even easier. Below we create two charts, with `e_datazoom`, hiding one of the latter. On the second chart we run `e_connect` to connect it with the other; sliders are now linked.

You can link charts together in two different ways, one with `e_connect` by refering other charts's id (`elementId`)

```{r}
e1 <- mtcars %>% 
  e_charts(
    mpg,
    height = 200,
    elementId = "chart1" # specify id
  ) %>% 
  e_scatter(wt) %>% 
  e_datazoom(show = FALSE) # hide

e2 <- mtcars %>% 
  e_charts(
    wt,
    height = 200,
    elementId = "chart2" # specify id
  ) %>% 
  e_scatter(qsec) %>% 
  e_datazoom(show = FALSE) # hide
  
e3 <- mtcars %>% 
  e_charts(
    qsec,
    height = 200
  ) %>% 
  e_scatter(hp) %>% 
  e_datazoom() %>% 
  e_connect(c("chart1", "chart2")) # connect
```

You can browse the above from your console like so.

```{r, eval = TRUE}
e_arrange(e1, e2, e3)
```

The package natively links interactions, therefore, in the following the legend is acutally unique, one legend will trigger on both charts because they bear the same name.

```{r}
e4 <- mtcars %>% 
    e_charts(
        mpg,
        height = 200,
        elementId = "chart" # specify id
    ) %>% 
    e_scatter(wt, name = "Click me!")

e5 <- mtcars %>% 
    e_charts(
        wt,
        height = 200
    ) %>% 
    e_scatter(qsec, name = "Click me!") %>% 
    e_connect("chart") # connect
```

```{r, eval = TRUE}
e_arrange(e4, e5)
```
