---
title: "Get Started"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to `echarts4r`, let's explore the package together.

1. All functions of the `echarts4r` package start with `e_`.
2. All its [Shiny](https://shiny.rstudio.com/) proxies end with `_p`. 
3. All `echarts4r` plots are initialised with `e_charts`.
4. All functions are `%>%` friendly.
5. Most functions have escape hatches ending in `_`.

### Your first plots

Let's build a line chart, load the library and pipe your data to `e_charts`. If you are not at ease with the `%>%` you can use `e_charts(mtcars, wt)`.

```{r}
library(echarts4r) # load echarts4r

mtcars %>% 
  e_charts(x = wt) %>% # initialise and set x
  e_line(serie = mpg) # add a line
```

If you are not at ease with bare column names you can use the escape hatches ending in `_`.

```{r, eval = FALSE}
mtcars %>% 
  e_charts_("wt") %>% 
  e_line_("mpg")
```

The easiest way is to use the `%>%` operator to add plots and options, we'll change the minimum of our x axis.

```{r}
mtcars %>% 
  e_charts(wt) %>% # initialise
  e_line(qsec) %>% # add line
  e_area(mpg) %>% # add area
  e_x_axis(min = 1) # change x axis minimum
```

We could also change the lines to make them `smooth`.

```{r}
mtcars %>% 
  e_charts(wt) %>% # initialise
  e_line(qsec, smooth = TRUE) %>% # add smooth line
  e_area(mpg, smooth = TRUE) %>% # add area
  e_x_axis(min = 1) # change x axis minimum
```

`qsec` and `mpg` isn't clear to reader, rename them, lets also label the x axis while we're at it.

```{r}
mtcars %>% 
  e_charts(wt) %>% # initialise
  e_line(qsec, smooth = TRUE, name = "1/4 mile time") %>% # add smooth line
  e_area(mpg, smooth = TRUE, name = "Miles/gallon") %>% # add area
  e_x_axis(min = 1, name = "weight") # change x axis minimum
```

We can use one of the 13 built-in themes, see `?e_theme` for a complete list, we'll also add a title with `e_title`.

```{r}
mtcars %>% 
  e_charts(wt) %>% # initialise
  e_line(qsec, smooth = TRUE, name = "1/4 mile time") %>% # add smooth line
  e_area(mpg, smooth = TRUE, name = "Miles/gallon") %>% # add area
  e_x_axis(min = 1, name = "weight") %>%  # change x axis minimum
  e_title("Ol' mtcars example") %>%  # Add title
  e_theme("infographic") # theme
```

The legend and title are a bit close, let's move the legend to another part the canvas.

```{r}
mtcars %>% 
  e_charts(wt) %>% # initialise
  e_line(qsec, smooth = TRUE, name = "1/4 mile time") %>% # add smooth line
  e_area(mpg, smooth = TRUE, name = "Miles/gallon") %>% # add area
  e_x_axis(min = 1, name = "weight") %>%  # change x axis minimum
  e_title("Ol' mtcars example") %>%  # Add title
  e_theme("infographic") %>%  # theme
  e_legend(bottom = 0) # move legend to the bottom
```

Add a tooltip, of which there are numerous [options](https://ecomfe.github.io/echarts-doc/public/en/option.html#tooltip), here we use `trigger = "axis"` to trigger the tooltip by the axis rather than a single data point.

```{r}
mtcars %>% 
  e_charts(wt) %>% # initialise
  e_line(qsec, smooth = TRUE, name = "1/4 mile time") %>% # add smooth line
  e_area(mpg, smooth = TRUE, name = "Miles/gallon") %>% # add area
  e_x_axis(min = 1, name = "weight") %>%  # change x axis minimum
  e_title("Ol' mtcars example") %>%  # Add title
  e_theme("infographic") %>% # theme
  e_legend(bottom = 0) %>% # move legend to the bottom
  e_tooltip(trigger = "axis") # tooltip
```

You can also customise the axis with `e_axis` or its sister functions, `e_x_axis` and `e_y_axis`. There are also helper functions like `e_format_axis` to easily add suffixes or prefixes to your axis labels.

```{r}
mtcars %>% 
  e_charts(wt) %>% # initialise
  e_line(qsec, smooth = TRUE, name = "1/4 mile time") %>% # add smooth line
  e_area(mpg, smooth = TRUE, name = "Miles/gallon") %>% # add area
  e_x_axis(min = 1, name = "weight") %>%  # change x axis minimum
  e_title("Ol' mtcars example") %>%  # Add title
  e_theme("infographic") %>% # theme
  e_legend(bottom = 0) %>%  # move legend to the bottom
  e_tooltip(trigger = "axis") %>%  # tooltip
  e_format_y_axis(suffix = "mpg")
```

You're in on the basics, go to the [advanced](articles/advanced.html) section or navigate the site to discover how add multiple linked graphs, draw on globes, use the package in shiny, and more.