---
title: "Graphics"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Graphics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(echarts4r)

e_common(
    font_family = "Raleway"
)
```

With `echarts4r` comes a small but powerful low level API to graphic elements.

## Functions

Graphic functions end in `_g`

- `g_graphic_g` (initialisation)
- `g_group_g`
- `g_image_g`
- `g_text_g`
- `g_rect_g`
- `g_circle_g`
- `g_ring_g`
- `g_sector_g`
- `g_arc_g`
- `g_polygon_g`
- `g_polyline_g`
- `g_line_g`
- `g_bezier_curve_g`

## Draft

The `e_draft` helper function is a very simple wrapper aroudn the graphics API and thus a good example of what can be achieved.

```{r}
cars |> 
  e_charts(speed) |> 
  e_scatter(dist) |>
  e_draft()
```

## Image

You can add an image for instance.

```{r}
cars |> 
  e_charts(speed) |> 
  e_scatter(dist) |>
  e_image_g(
    right = 20,
    top = 20,
    z = -999,
    style = list(
      image = "https://www.r-project.org/logo/Rlogo.png",
      width = 150,
      height = 150,
      opacity = .6
    )
  )
```