---
title: "Grid & Axis"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Grid & Axis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(echarts4r)

e_common(
    font_family = "Raleway"
)
```

`echarts4r` comes with a highly customisable grid and axis, but admittedly they take some getting used to.

## Axis helper

You can customise the axis with `e_axis`, `e_x_axis` or `e_y_axis`, you can see the [official documentation](https://echarts.apache.org/en/option.html#xAxis) for more details. There is also a helper function, `e_format_axis` and its sisters `e_format_x_axis` and `e_format_y_axis`. The latter lets you easily add suffix or prefix to your axis labels.

Say you want to plot against ceslius.

```{r}
df <- data.frame(
  x = 1:20, # celsius
  y = runif(20, 1, 100) # percentages
)

df |> 
  e_charts(x) |> 
  e_line(y) |> 
  e_format_x_axis(suffix = "°C") |> 
  e_legend(FALSE)
```

Since version `0.2.1` you can also easily format the axis to decimal, percentages or currencies thanks to contribution from [Artem Klevtsov](https://github.com/artemklevtsov).

```{r}
df |> 
  dplyr::mutate(y = y / 100) |> 
  e_charts(x) |> 
  e_line(y, legend = FALSE) |> 
  e_x_axis(
    formatter = e_axis_formatter("currency", currency = "GBP")
  ) |> 
  e_y_axis(
    formatter = e_axis_formatter("decimal", digits = 3)
  )
```

## Grid

You can also customise the grid to have, for instance, multiple plots on one canvas.

Let's initialise a basic plot.

```{r}
df <- data.frame(
  x = 1:20, 
  w = runif(20, 1, 100),
  z = runif(20, 25, 75)
)

df |> 
  e_charts(x) |> 
  e_line(w) |> 
  e_line(z)
```

Now say we don't want `w` and `z` on the same plot. We could of course make two entirely different plots (2 plots initialised with `e_charts()`), but it would be cleaner to have them on the same canvas, a bit like [ggplot2 facets](http://ggplot2.tidyverse.org/reference/facet_grid.html).

First two plots on the same canvas means multiple axis, so we'll plot each serie on its own axis.

`echarts4r` is an R API to a JavaScript library, so arrays start at one; `x` and `y` indices default to 0 so we only need to change one of the series' indices to 1. Therefore one serie is plotted on index 0 and the other on index 1 for two `x`and `y` axis.

```{r}
df |> 
  e_charts(x) |> 
  e_line(w) |> 
  e_line(z, x_index = 1, y_index = 1)
```

Notice how `echarts4r` puts the additional axis on the top and right of the plot. This is a useful feature but not what we want; we're missing a split grid.

We use `e_grid` twice for two grids, we define the height of each; `35%` is ideal for stacked grids, you need some margin for the legend, the axis, etc. hence not using `50%`. 

```{r}
df |> 
  e_charts(x) |> 
  e_line(w) |> 
  e_line(z, x_index = 1, y_index = 1) |> 
  e_grid(height = "35%") |> # two grids of 35% height
  e_grid(height = "35%", top = "50%") # this grid is 50% from the top
```

However, we still have both line plots on the same grid. Here is how to think about grids and axis in `echarts4r`. 

1. Your series (i.e.: `e_line`) are plotted against axis (`e_axis`)
2. These axis are plotted in grids `e_grid`

So we have two grids and two axis but the axis are both plotted on the same grid(point #2 above). So we need to move our two additional axis to another grid. Note that grid indices also start at 0 here.

```{r}
df |> 
  e_charts(x) |> 
  e_line(w) |> 
  e_line(z, x_index = 1, y_index = 1) |> 
  e_grid(height = "35%") |> 
  e_grid(height = "35%", top = "50%") |> 
  e_y_axis(gridIndex = 1) |> # put x and y on grid index 1
  e_x_axis(gridIndex = 1)
```

There you go!

You can also have a different grid to put the plots side by side.

```{r}
df |> 
  e_charts(x) |> 
  e_line(w) |> 
  e_line(z, x_index = 1, y_index = 1) |> 
  e_grid(width = "35%") |> 
  e_grid(width = "35%", left = "55%") |> 
  e_y_axis(gridIndex = 1) |> # put x and y on grid index 1
  e_x_axis(gridIndex = 1)
```

## Why bother?

Well now those charts can share interactions.

```{r}
df |> 
  e_charts(x) |> 
  e_line(w) |> 
  e_line(z, x_index = 1, y_index = 1) |> 
  e_grid(height = "35%") |> 
  e_grid(height = "35%", top = "50%") |> 
  e_y_axis(gridIndex = 1) |> 
  e_x_axis(gridIndex = 1) |> 
  e_tooltip(trigger = "axis") |> 
  e_datazoom(x_index = c(0, 1)) # add data zoom for for x axis
```

## Axis

You can also mess with the axis to completely change your chart. For instance, from a regular bar chart:

```{r}
df <- data.frame(
  x = LETTERS[1:10], 
  y = seq(1, 20, by = 2),
  z = runif(10, 5, 20)
)

df |> 
  e_charts(x) |> 
  e_bar(y)
```

to a polar chart.

```{r}
df |> 
  e_charts(x) |> 
  e_polar() |> 
  e_angle_axis(x) |> # angle = x
  e_radius_axis() |> 
  e_bar(y, coord_system = "polar")
```

or a radial chart one.

```{r}
df |> 
  e_charts(x) |> 
  e_polar() |> 
  e_angle_axis() |> 
  e_radius_axis(x) |> # radius = x 
  e_bar(y, coord_system = "polar")
```

This will also work with other chart types.

```{r}
df |> 
  e_charts(x) |> 
  e_polar() |> 
  e_angle_axis() |> 
  e_radius_axis(x) |> 
  e_line(y, coord_system = "polar") |> 
  e_scatter(z, coord_system = "polar")
```
