---
title: "GeoJSON data"
author: "Pengfei Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GeoJSON data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(echarts4r)

e_common(
    font_family = "Raleway"
)
```

## Introduction

You will find _215 maps_ in the companion package [echarts4r.maps](https://echarts4r-maps.john-coene.com/). However, since you may need different kinds of maps i.e.: at the citiy or county level that are not included in this package, you may need to get the detailed map data from third-party source such as [gadm.org](https://gadm.org/). This document shows how to make your own `GeoJSON` file which can be used in `e_map_register`.

## Packages

These are packages to help you building such maps

- `sp`: spatial data management package.
- `raster`:  get spatial data from [gadm.org](https://gadm.org/).
- `geojsonio`:  convert spatial data into json format.
- `rmapshaper`: simplify the spatial data.

```{r}
library(echarts4r)
library(sp)
library(raster)
library(geojsonio)
library(rmapshaper)
```

## Example

Get India map data from gadm website, this command need network available, it will download the rds data to the current directory.

```{r}
india_sp <- raster::getData('GADM', country = 'INDIA', level = 2) 
india_sp |> 
  head() |> 
  knitr::kable()
```

Note that you can then combine maps with `raster::union(map1, map2)` or with the `em_maps` function from the [echarts4r.maps](https://echarts4r-maps.john-coene.com) package. Then convert the `SpatialPolygonsDataFrame` into `GeoJSON` with `geojsonio`: _this will take a long time as the map is very detailed_.

```{r}
india_json <- geojsonio::geojson_list(india_sp)
print(object.size(india_json), units = "Mb")
```

Therefore we can simplify the map to make it smaller.

```{r}
india_small <- rmapshaper::ms_simplify(india_sp, keep = 0.05) 
india_json_small <- geojsonio::geojson_list(india_small)
print(object.size(india_json_small), units = "Mb") 
```

The function `raster::getData` gives each polygon a `NAME_*` property (where `*` is the `level` specified) rather than just `name`. The tooltip will not display properly unless we use the `nameMap` to point to that property, by default echarts expects the `name` property.

Now we can use the `GeoJSON` with `e_map_register`.

```{r}
# plot 
e_charts() |>
  e_map_register("India", india_json_small) |>
  e_map(map = "India", nameProperty = "NAME_2")
```





