---
title: "Mark Points, Lines & Areas"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mark Points, Lines & Areas}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
library(echarts4r)

e_common(
    font_family = "Raleway"
)
```

You can mark points, lines and areas on your chart to emphasise certain things.



## Type

You mark things by passing a `list` to the `data` argument, this list can be of many different format, see the [official documentation](https://echarts.apache.org/en/option.html#series-line.markPoint.data).

One of the format is to pass a `type`:

- `min`
- `max`
- `avg`

```{r}
max <- list(
  name = "Max",
  type = "max"
)

min <- list(
  name = "Min",
  type = "min"
)

avg <- list(
  type = "average",
  name = "AVG"
)
```

By default `e_mark_*` is applied to all series.

```{r}
iris |> 
  group_by(Species) |> 
  e_charts(Sepal.Length) |> 
  e_line(Sepal.Width) |> 
  e_mark_point(data = max) |> 
  e_mark_point(data = min) |> 
  e_mark_point(data = avg)
```

But you can specify one or more serie it should apply apply to.

```{r}
iris |> 
  group_by(Species) |> 
  e_charts(Sepal.Length) |> 
  e_line(Sepal.Width) |> 
  e_mark_point(serie = "setosa", data = max) |> 
  e_mark_point(serie = c("virginica", "setosa"), data = min) |> 
  e_mark_point(serie = c("virginica", "versicolor"), data = avg)
```

## Custom

```{r}
library(dplyr)

# get a random point
(
  point <- iris |> 
    filter(Species == "setosa") |> 
    sample_n(1) |>  
    select(
      xAxis = Sepal.Length,
      yAxis = Sepal.Width,
      value = Petal.Width
    ) |> 
    as.list()
)

iris |> 
  group_by(Species) |> 
  e_charts(Sepal.Length) |> 
  e_line(Sepal.Width) |> 
  e_mark_point(serie = "setosa", data = point) |> 
  e_x_axis(min = 4)
```

## Point

```{r}
iris |> 
  group_by(Species) |> 
  e_charts(Sepal.Length) |> 
  e_line(Sepal.Width) |> 
  e_mark_point(data = avg) |> 
  e_x_axis(min = 4)
```

## Line

Horizontally.

```{r}
iris |> 
  group_by(Species) |> 
  e_charts(Sepal.Length) |> 
  e_line(Sepal.Width) |> 
  e_mark_line(data = avg) |> 
  e_x_axis(min = 4)
```

Vertically.

```{r}
cars |> 
  e_charts(speed) |> 
  e_scatter(dist, symbol_size = 5) |> 
  e_legend(FALSE) |> 
  e_mark_line(data = list(xAxis = 7), title = "Tortoise") |> 
  e_mark_line(data = list(xAxis = 12), title = "Speed Limit") |> 
  e_mark_line(data = list(xAxis = 22), title = "Need for Speed") 
```

## Area

```{r}
iris |> 
  group_by(Species) |> 
  e_charts(Sepal.Length) |> 
  e_line(Sepal.Width) |> 
  e_mark_area(
    data = list(
      list(xAxis = "min", yAxis = "min"), 
      list(xAxis = "max", yAxis = "max")
    )
  ) |> 
  e_x_axis(min = 4)
```