---
title: "Timeline"
author: "John Coen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
library(quantmod)
options("getSymbols.warning4.0"=FALSE)
options("getSymbols.yahoo.warning"=FALSE)
library(echarts4r)
```

`echarts4r` version `0.2.1` supports the timeline component!

```{r}
# fake data
df <- data.frame(
  year = c(
    rep(2016, 25),
    rep(2017, 25),
    rep(2018, 25),
    rep(2019, 25)
  ),
  x = runif(100, 1, 10),
  y = runif(100, 5, 35),
  grp = c(
    rep("A", 50),
    rep("B", 50)
  )
)
```

With the phoney data:

```{r}
df %>% 
  group_by(year) %>% 
  e_charts(x, timeline = TRUE) %>% 
  e_scatter(y)
```

It works with most chart types.

```{r}
df %>% 
  group_by(year) %>% 
  e_charts(x, timeline = TRUE) %>% 
  e_scatter(y) %>% 
  e_loess(y ~ x)
```

You can pass options to the timeline with `e_timeline_opts`.

```{r}
library(dplyr)
library(echarts4r.maps)

df <- USArrests

# scale 0 to 1
.scl <- function(x){
    (x - min(x)) / (max(x) - min(x))
}

df %>% 
  mutate(
      State = row.names(.),
      Rape = .scl(Rape),
      Murder = .scl(Murder),
      Assault = .scl(Assault)
  ) %>% 
  select(State, Rape, Murder, Assault) %>% 
  group_by(State) %>% 
  tidyr::gather("Key",  "Value", Murder, Rape, Assault) %>% 
  group_by(Key) %>% 
  e_charts(State, timeline = TRUE) %>% 
  em_map("USA") %>% 
  e_map(Value, map = "USA") %>% 
  e_visual_map(min = 0, max = 1) %>% 
  e_timeline_opts(autoPlay = TRUE)
```

The function `e_timeline_opts` is used to set general options on the timeline, i.e.: auto-play like above. The full list of options is on the [official website](https://ecomfe.github.io/echarts-doc/public/en/option.html#timeline).

However, we can also set options specific to each timestep with `e_timeline_serie`. The arguments to this function differ quite a bit from the rest of the package. As we have to assign options to multiple timesteps at once we need to pass vectors or lists of options, the length of the timesteps.

```{r}
library(quantmod)

getSymbols(c("GS", "GOOG")) # Goldman Sachs & Google
GS <- as.data.frame(GS)
GOOG <- as.data.frame(GOOG)

colnames <- c("Open", "High", "Low", "Close", "Volume", "Adjusted")
names(GS) <- colnames
names(GOOG) <- colnames

GS$sym <- "GS"
GOOG$sym <- "GOOG"

data <- bind_rows(GS, GOOG)
data$date <- rep(row.names(GS), 2)

data %>% 
  group_by(sym) %>% 
  e_charts(date, timeline = TRUE) %>% 
  e_candle(Open, Close, Low, High, legend = FALSE) %>% 
  e_y_axis(max = 1500) %>% 
  e_tooltip(trigger = "axis") %>% 
  e_timeline_opts(playInterval = 1000) %>% 
  e_timeline_serie(
    title = list(
      list(text = "Goldman Sachs"),
      list(text = "Google")
    )
  )
```
